Rule-Based Preordering on Multiple Syntactic Levels \\in Statistical Machine Translation

### 2014-09-26 Paper/paper.tex
.

\begin{document}
\maketitle
%
\begin{abstract}
We propose a novel data-driven rule-based preordering approach, which uses the tree information of multiple syntactic levels. This approach extend the tree-based reordering from one level into multiple levels, which has the capability to process more complicated reordering cases. We've conducted experiments in English-to-Chinese and Chinese-to-English translation directions. Our results show that the approach has led to improved translation quality both when it was applied separately or when it was combined with some other reordering approaches. As our reordering approach was used alone, it showed an improvement of $1.61$ in BLEU score in the English-to-Chinese translation direction and an improvement of $2.16$ in BLEU score in the Chinese-to-English translation direction, in comparison with the baseline, which used no word reordering. As our preordering approach were combined with the short rule \cite{short}, long rule \cite{long} and tree rule \cite{tree} based preordering approaches, it showed further improvements of up to $0.43$ in BLEU score in the English-to-Chinese translation direction and further improvements of up to $0.3$ in BLEU score in the Chinese-to-English translation direction. Through the translations that used our preordering approach, we've also found many translation examples with improved syntactic structures.

@@

Most state-of-the-art phrase-based SMT systems use language model, phrase table or decoder to adjust the word order. Or an additional reordering model is used in the log-linear model for word reordering. However, these methods may have some disadvantages, such as some don't handle long-distance reordering, some don't handle unstructured reordering and some are rather time-consuming.

@@

For the other, both languages have sometimes very different sentence structures. Thus, a word-for-word translation between English and Chinese is often unnatural or difficult to understand. Each of them has some sentence patterns that don't exist or rarely used in the other. In Chinese, a modifier is often put before the part that it modifies. While in English, it is very common that the modifier is put after the part that it modifies. Besides, English sentences with a lot of long clauses may be more suitable to translate into several Chinese sentences, because in Chinese people don't tend to use long clauses in general.

@@

We have also found improvements in the sentence structure. Table~\ref{t1} and Table~\ref{t2} show some translation examples in both translation directions. Sections are separated by double lines in the table. Each section of this table shows one translation example with the source sentence (\emph{source}), translation without using MLT reordering (\emph{no MLT}), translation with MLT reordering (\emph{MLT}) and the reference (\emph{reference}). \emph{Glossary} for the source sentences or references in Chinese is also added as word for word translation. Each word or group of hyphenated words in the glossary corresponds a Chinese character or a group of Chinese characters that are not separated with space. A placeholder $\Box$ is used to replace words that are difficult to translate, which play grammatical roles generally. The translation without using MLT reordering comes from the configuration with highest BLEU score that didn't use MLT reordering. And the translation with MLT reordering comes from the configuration with highest BLEU score that used MLT reordering. From the examples, we can clearly see the improvements in sentence structure.

@@

By taking a close look at the gap between the scores of oracle reordering and the best scores achieved by MLT reordering, we can also see, there's still potential for improvements of translation between English and Chinese through better reordering methods.

>>>>

\begin{document}
\maketitle
%
\begin{abstract}
We propose a novel data-driven rule-based preordering approach, which uses the tree information of multiple syntactic levels. This approach extend the tree-based reordering from one level into multiple levels, which has the capability to process more complicated reordering cases. We have conducted experiments in English-to-Chinese and Chinese-to-English translation directions. Our results show that the approach has led to improved translation quality both when it was applied separately or when it was combined with some other reordering approaches. As our reordering approach was used alone, it showed an improvement of $1.61$ in BLEU score in the English-to-Chinese translation direction and an improvement of $2.16$ in BLEU score in the Chinese-to-English translation direction, in comparison with the baseline, which used no word reordering. As our preordering approach were combined with the short rule \cite{short}, long rule \cite{long} and tree rule \cite{tree} based preordering approaches, it showed further improvements of up to $0.43$ in BLEU score in the English-to-Chinese translation direction and further improvements of up to $0.3$ in BLEU score in the Chinese-to-English translation direction. Through the translations that used our preordering approach, we have also found many translation examples with improved syntactic structures.

@@

Most state-of-the-art phrase-based SMT systems use language model, phrase table or decoder to adjust the word order. Or an additional reordering model is used in the log-linear model for word reordering. However, these methods may have some disadvantages, such as some do not handle long-distance reordering, some do not handle unstructured reordering and some are rather time-consuming.

@@

For the other, both languages have sometimes very different sentence structures. Thus, a word-for-word translation between English and Chinese is often unnatural or difficult to understand. Each of them has some sentence patterns that do not exist or rarely used in the other. In Chinese, a modifier is often put before the part that it modifies. While in English, it is very common that the modifier is put after the part that it modifies. Besides, English sentences with a lot of long clauses may be more suitable to translate into several Chinese sentences, because in Chinese people do not tend to use long clauses in general.

@@

We have also found improvements in the sentence structure. Table~\ref{t1} and Table~\ref{t2} show some translation examples in both translation directions. Sections are separated by double lines in the table. Each section of this table shows one translation example with the source sentence (\emph{source}), translation without using MLT reordering (\emph{no MLT}), translation with MLT reordering (\emph{MLT}) and the reference (\emph{reference}). \emph{Glossary} for the source sentences or references in Chinese is also added as word for word translation. Each word or group of hyphenated words in the glossary corresponds a Chinese character or a group of Chinese characters that are not separated with space. A placeholder $\Box$ is used to replace words that are difficult to translate, which play grammatical roles generally. The translation without using MLT reordering comes from the configuration with highest BLEU score that did not use MLT reordering. And the translation with MLT reordering comes from the configuration with highest BLEU score that used MLT reordering. From the examples, we can clearly see the improvements in sentence structure.

@@

By taking a close look at the gap between the scores of oracle reordering and the best scores achieved by MLT reordering, we can also see, there is still potential for improvements of translation between English and Chinese through better reordering methods.
